HSC Synthetic Pipeline I: Basic Design and Characterization of HSC Photometric Performance

### 2017-04-14 draft/ms_v2.tex
Minor update; change the version number
Song: Fix abstract

% Version 0; Only rough outline by SH
% Version 1; First draft by SH

@@

   The Subaru Strategic Program (SSP) is an ambitious wide-area, multi-band
    survey using the Hyper Suprime-Cam (HSC) on the Subaru telescope.
      At SSP's imaging depth \susan{quantify?}, it is challenging to achieve accurate,
    unbiased, and consistent photometry across all five bands. To improve data processing and achieve accurate photometric measurements, we have developed
   \synpipe{}, a \texttt{Python}-based, flexible framework
    that interfaces with the HSC data reduction pipeline (\hscpipe{}) to process data from the first public HSC--SSP data release. \susan{I expected to see something in the abstract that clarifies why this is Pipeline I; does this suggestion accomplish that?} We test  \synpipe{}
    performance by injecting synthetic objects into single-\texttt{visit} HSC images.
    We use coadded images in two Wide layer \tracts{} with representative
    seeing conditions to demonstrate  \synpipe{} implementation and to examine  \texttt{hscpipe}'s 
    general photometric performance.
    We find that uncertainties of HSC \forced{} PSF photometry for stars typically
    range from ${\sim}0.01$ mag at $i{\sim}18.0$ mag to ${\sim}0.06$ at $i{\sim}25.5$
    mag (1\%-7\% accuracy in the $i$-band). 
    For synthetic galaxies based on a single-\ser{} model, uncertainties of the
    forced \cmodel{} photometry typically range from 0.14 mag at $i{\sim}20.0$ mag to
    0.20 mag at $i{\sim} 25.2$ mag.
    Over the color and magnitude ranges used in the  \synpipe{} tests, we find that both 
    \forced{} PSF and \cmodel{} photometry provide unbiased color estimates that 
    are robust in different seeing conditions.
    We also notice a few issues in the current \hscpipe{} that are worth keeping
    in mind when using HSC data: 
    1) The degree to which an object is blended with others impacts the photometric 
    accuracy, especially for point sources.
    Highly blended objects tend to have larger photometric uncertainty, systematically
    underestimated flux, and slightly biased color.
    2) A relatively high fraction of faint stars (${\sim}16$\% at $i>22.5$ mag) can be
    misclassified as extended objects.
    3) The shape and size estimates for galaxies using \cmodel{} suffer from strong
    biases.

>>>>

% Version 0; Only rough outline by SH
% Version 1; First draft by SH
% Version 2; Main text is finished; with edits from Susan Foster

@@

    The Subaru Strategic Program (SSP) is an ambitious wide-area, multi-band survey 
    using the Hyper Suprime-Cam (HSC) on the Subaru telescope.
    As SSP reaches to detection limit of $i>26.0$ mag in the Wide field, it is 
    challenging to achieve accurate, unbiased, and consistent photometry across all 
    five bands.
    To improve data processing and achieve accurate photometric measurements, we have 
    developed \synpipe{}, a \texttt{Python}-based, flexible framework that interfaces 
    with the HSC data reduction pipeline (\hscpipe{}) to process data from the first 
    public HSC--SSP data release. 
    In the first paper of this series, we explain the design and implementation of 
    \synpipe{}, and use coadd images in two Wide layer \tracts{} with representative 
    seeing conditions to examine the photometric performance of \hscpipe{}.
    We find that uncertainties of HSC \forced{} PSF photometry for stars typically
    range from ${\sim}0.01$ mag at $i{\sim}18.0$ mag to ${\sim}0.06$ at $i{\sim}25.5$
    mag (1\%-7\% accuracy in the $i$-band). 
    For synthetic galaxies based on a single-\ser{} model, uncertainties of the
    forced \cmodel{} photometry typically range from 0.14 mag at $i{\sim}20.0$ mag 
    to 0.20 mag at $i{\sim} 25.2$ mag.
    Over the color and magnitude ranges used in these \synpipe{} tests, we find that 
    both \forced{} PSF and \cmodel{} photometry provide unbiased color estimates 
    that are robust in different seeing conditions.
    We also notice a few issues in the current \hscpipe{} that are worth keeping
    in mind when using HSC data: 
    1) The degree to which an object is blended with others impacts the photometric 
    accuracy, especially for point sources.
    Highly blended objects tend to have larger photometric uncertainty, systematically
    underestimated flux, and slightly biased color.
    2) A relatively high fraction of faint stars (${\sim}16$\% at $i>22.5$ mag) can be
    misclassified as extended objects.
    3) The shape and size estimates for galaxies using \cmodel{} suffer from strong
    biases.
